Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
Revise abstract further.

\begin{document}
\maketitle
\begin{abstract}
We use a recursive neural network (RNN) on a part-of-speech tagging task (POS). We propose and implement two models: a basic RNN and a Compositional Vector Tagger (CVT) RNN. The performance of the basic RNN is close to the HMM model and with high probability will beat it if capitalization information is captured. The intractable tagging time of the CVT model means we cannot analyze it. We tried some useful neural network training tricks and carefully analyze the performance of the basic RNN model, such as verifying the contribution of sequential information and error rates of different parts of sentences.
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
We use a recursive neural network (RNN) on a part-of-speech tagging task (POS). We propose and implement two models: a basic RNN and a Compositional Vector Tagger (CVT) RNN. The performance of the basic RNN is close to the HMM model and will likely beat it if capitalization information is captured. The intractable tagging time of the CVT model means we cannot analyze it. We tried some useful neural network training tricks and carefully analyze the performance of the basic RNN model, by verifying the contribution of sequential information and error rates of different parts of sentences.
\end{abstract}
